---
title: 'STA426: Exercise 1'
author: "Alvaro Ingold Alfonso"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Excercise 1.1

A GitHub repository with the appropriate README.md file has been created and can be accessed by clicking [\textcolor{blue}{here}](https://github.com/alvaroing12/sta426exercises).

## Excercise 1.2

### Data sampling
100 values are sampled from a log-normal distribution with mean $\mu$ = 1 and standard deviation $\sigma$ = 0.25, and stored in a vector "x".

```{r sampleValues, echo=TRUE}
x <- rlnorm(n = 100, meanlog = 1, sdlog = 0.25)
```
  
### Histogram  
To show the distribution of the sampled values, a histogram is plotted using the code below:

```{r plotHistogram, echo=TRUE}
hist(x = x, main = "Histogram of sample", breaks = 10)
```

The resulting sample has a mean $\mu$ = `r round(mean(x), 3)` and a variance $\sigma^2$ = `r round(var(x), 3)`.
  
### Histogram on the log scale
To show the distribution of the sampled values on the logarithmic scale, first the _log_ function must be applied to each element of the vector "x", and the resulting values are stored in a new vector called "xlog". Afterwards a histogram of "xlog" is plotted as usual.

```{r plotHistogramLogScale, echo=TRUE}
xlog <- log(x)
hist(x = xlog, main = "Histogram of sample on log scale", breaks = 10, xlab = "log(x)")
```

The resulting sample on log scale has a mean $\mu$ = `r round(mean(xlog), 3)` and a variance $\sigma^2$ = `r round(var(xlog), 3)`.